---
title: "Visualizations"
author: "Data Science Project"
date: "September 9, 2017"
output: html_document
---
####Visualizations Basics####

This is a file for the basics of visualisations.

```{r}
library(ISwR)
juulData=juul

str(juulData)
head(juulData)
tail(juulData)
```

##Histogram##

```{r}
hist(juulData$igf1,breaks = 45,col = "pink",xlab= "Insulin Growth Factor",main = "IGF Distribution",xlim = c(0,1000),ylim = c(0,60))
```

## Pie Chart

```{r}
library(datasets)
##write.csv(mtcars,file = "mtCars.csv")```{r}


library(readr)
mtCarsData <- read_csv("R:/Data Science Project (DSP)/mtCars.csv")


##mtcarsdata= file.choose()
str(mtCarsData)
summary(mtCarsData)
pie(table(mtCarsData$`Car Names`))

plot(mtCarsData$mpg,mtCarsData$disp)
```

##BoxPlot

```{r}
boxplot(mtCarsData$mpg~mtCarsData$`Car Names`)


```

##Scatter Plot

```{r}
plot(mtCarsData$mpg~mtCarsData$wt,col="red")
```

Linear regression for example

```{r}
 linear = lm(mtCarsData$mpg~mtCarsData$cyl+mtCarsData$wt,mtCarsData)

plot(linear)
```


##Pairs Plot##
```{r}
summary(mtCarsData)
pairs(mtCarsData[2:5])
```
#ScatterPlot##

```{r}
library(scatterplot3d)
scatterplot3d(iris$Petal.Width,iris$Sepal.Length,iris$Sepal.Width)

```

##Contour Plot

```{r}
library(lattice)
filled.contour(volcano,color= terrain.colors,asp=1,plot.axes = contour(volcano,add = T))
```

```{r}
persp(volcano,theta = 25,phi = 30,expand = 0.5,col = "lightblue")
```

